Clustering time series based on probability distributions across temporal granularities

### 2021-11-18 main.Rmd
filled all XXX except for Discusssion

<!-- In Figure \ref{fig:opt-cluster-tsne-jsd}, the $sindex$ is plotted against the number of clusters for clustering based on wpd-based distances. The scales are very different from those used in JS-based clustering. The $sindex$ falls from around $20$ when $k=3$ to $19$ when $k=4$ and further decreases to $17.5$ with $k>7$. Thus, there are few choices available for the number of clusters.--> Figure \ref{fig:summary-plot-wpd} whos the wpd values for the three different granularities of the 24 customers, coloured by the 6 cluster solution. XXX REWORK THIS WHEN NEW CLUSTER RESULTS ARE SHOWN<!--The groupings with $k=4$ is shown through a parallel coordinate plot with the three significant cyclic granularities. The variables are sorted according to their separation across classes (rather than their overall variation between classes). This means that $moy$ is the most important variable in distinguishing the groups, followed by $hod$ and $wnwd$. The two customers (id: 16 and 18) that have significant differences between $wnwd$ categories (in Figure \ref{fig:hod-ind-group-png}) stand out from the rest of the customers. Group-4 has a higher $wpd$ for $hod$ than $moy$ or $wnwd$. Group-2 and Group-3 have the most distinct patterns across $moy$. Group-1 is a mixed group that has strong patterns on at least one of the three variables. When $k=3$ is used, Group-2 and Group-3 are merged because their patterns relative to $moy$, $hod$ and $wnwd$ are the same. The findings vary from JS-based clustering, yet it is a helpful grouping.-->

>>>>

<!-- In Figure \ref{fig:opt-cluster-tsne-jsd}, the $sindex$ is plotted against the number of clusters for clustering based on wpd-based distances. The scales are very different from those used in JS-based clustering. The $sindex$ falls from around $20$ when $k=3$ to $19$ when $k=4$ and further decreases to $17.5$ with $k>7$. Thus, there are few choices available for the number of clusters. Figure \ref{fig:summary-plot-wpd} whos the wpd values for the three different granularities of the 24 customers, coloured by the 6 cluster solution. XXX REWORK THIS WHEN NEW CLUSTER RESULTS ARE SHOWN<!--The groupings with $k=4$ is shown through a parallel coordinate plot with the three significant cyclic granularities. The variables are sorted according to their separation across classes (rather than their overall variation between classes). This means that $moy$ is the most important variable in distinguishing the groups, followed by $hod$ and $wnwd$. The two customers (id: 16 and 18) that have significant differences between $wnwd$ categories (in Figure \ref{fig:hod-ind-group-png}) stand out from the rest of the customers. Group-4 has a higher $wpd$ for $hod$ than $moy$ or $wnwd$. Group-2 and Group-3 have the most distinct patterns across $moy$. Group-1 is a mixed group that has strong patterns on at least one of the three variables. When $k=3$ is used, Group-2 and Group-3 are merged because their patterns relative to $moy$, $hod$ and $wnwd$ are the same. The findings vary from JS-based clustering, yet it is a helpful grouping.-->

Figure \ref{fig:summary-plot-wpd} shows the $wpd$ values $hod$, $moy$, and $wnwd$ of the $24$ customers, colored by $3$ (a) and $5$ (b) cluster solution as suggested by Figure \ref{fig:opt-cluster-tsne-jsd} through a parallel coordinate plot. The variables are 
standardized prior to clustering using WPD. In the display, the variables are sorted according to their separation across groups. This means that $wnwd$ is the most important variable in distinguishing the groups, followed by $hod$ and $moy$ for both (a) and (b).
Group P-1 and P-2 correspond to Q-1 and Q-2 respectively. Cluster P-3 splits into Q-3, Q-4 and Q-5. Customers 16 and 18 are characterized by unusual high values of $wpd$ on $wnwd$ compared to the rest of the customers and hence form a group. This could again be verified from figure \ref{fig:hod-ind-group-png}, where these were the only two customers with a difference in their $wnwd$ behavior. They are represented by P-1. P-2 has lower $wpd$ for $hod$ than $moy$ and $wnwd$. This can also be verified from Table \ref{tab:summary-table-wpd} where $hod$ has very low median values of $wpd$ over the members in the cluster, implying, at least half of these customers do not have an interesting $hod$ pattern. P-3 behaves exactly opposite to P-2 with higher $wpd$ for $hod$ compared to $moy$ and $wnwd$. These are the customers who have some significant pattern across $hod$ and this can again be validated by looking at \ref{fig:hod-ind-group-png}.
For $5$ cluster solution, this groups gets split into Q3-Q5 characterizing different relative significance over $moy$ and $wnwd$. For example, Q-4 and Q-5 have almost no pattern across $moy$, but Q-3 has a $moy$ pattern and thus it is reasonable to split them. The patterns could be different, but they are significant. Q-4 and Q-5 are separated because of their significance across $hod$.
